Computer Science House By-Laws

### 2014-05-16 articles.tex
removed debug flag
housing eval, alumni membership, quorum fix

% This package is useful for debugging label problems 
% Comment out in final revision
\usepackage{showkeys}

@@

\asubsection{ Non-Semantic Changes}
Any non-semantic change to the Constitution should be presented to the House for discussion. After the discussion an immediate House vote is taken. A quorum of fifty percent of the number of all House members eligible to vote must be present in order for the vote to be official. A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week. The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}. The ballots are collected for a minimum of a forty-eight hour period. A quorum of two-thirds of the number of all House members eligible to vote must cast ballots for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}. There must be a quorum of eighty-five percent of the number of all House members eligible to vote for the vote to be official. A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

@@

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting. If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately. The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Resignations}
An Active Member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Alumni who depart house for any reasons other than failure of the Membership Evaluation process, are considered to be in good standing. All other alumni are considered to be in bad standing.
\\*\\*
Active Members who depart house prior to the Membership evaluation will be an alumni in bad standing. The member may appeal to the Executive Board for an exemption based on their circumstances. 
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

@@

	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting. A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official. All winners are notified of their election, and they immediately assume the office for the term of the election. Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.

@@

\asection{Impeachment}
\begin{enumerate}
	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
	\item The impeachment petition is then presented at an Executive Board Meeting. The member(s) initiating the petition present their case to the Executive Board. The Executive Board then questions the accused member of the allegations.
	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment. If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed. This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office. Votes shall be collected and counted as described in \ref{Balloted Vote}.
	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office. If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position. A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
\end{enumerate}

@@

% ARTICLE V - VOTING
\article{Voting}
This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
\asection{Definitions}
\asubsection{Total Number of Possible Votes}
The Total Number of Possible Votes is defined as the number of possible votes that can be cast in a single vote.
\asubsubsection{House Vote} 
The sum of the number of Active members.
\asubsubsection{Executive Board Vote} 
The number of voting Executive Board directorships.
\asubsection{Total Number of Votes Cast}
The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
\asubsection{Quorum}
A Quorum is defined by the minimum number of votes cast required for a vote to be official. It is a fraction or a percentage of the total number of possible votes. Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention. A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
\asubsection{Proxy Ballot}
A Proxy Vote is defined as any ballot that was cast by one member on behalf of another member. Any member may cast a Proxy Vote for another member who is unable to actually participate in the vote. A Proxy Vote must be explicitly written down and signed by the member not in attendance. The count of all Proxy Vote must be recorded and announced in all votes. Proxy Votes are only permissible where explicitly stated, at the discretion of the person chairing the vote.
\asubsection{Abstention}
An Abstention is defined as a vote indicating a neutral position in the vote. A means to abstain must always be provided in a vote. Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
\asubsection{Vote Counters}
Vote Counters are the chairperson of the vote, and two randomly selected members.

>>>>

% This package is useful for debugging label problems 
% Comment out in final revision
%\usepackage{showkeys}

@@

\asubsection{ Non-Semantic Changes}
Any non-semantic change to the Constitution should be presented to the House for discussion. After the discussion an immediate House vote is taken.A quorum of fifty percent of the Total Number of Possible Votes must be present in order for the vote to be official. A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting. Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week. The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}. The ballots are collected for a minimum of a forty-eight hour period. A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official. A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution. The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}. There must be a There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official. A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

@@

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and the most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting. If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately. The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum. Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.  Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Resignations}
An Active Member may resign by submitting in writing the reason for resignation to the Chairman, or Evaluations Director.  The resignation will take effect immediately.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns, fails the Evaluation Process, or changes membership status.

\asection{Alumni Membership}
\asubsection{Alumni Membership Qualifications}
Alumni Membership is open to all former Active members of Computer Science House who passed at least one Membership Evaluation and departed for reasons other than revocation of House Membership.
\asubsection{Alumni Membership Selection}
Active members who depart house (i.e. resign) after passing the current operating session's Membership Evaluations are considered to be Alumni in good standing.
\\*\\*
Active members who depart house without passing the current operating session's Membership Evaluations are considered to be Alumni in bad standing. This may be appealed to the Executive Board in order to pursue a different outcome.
\asubsection{Alumni Membership Expectations}
There are no expectations associated with the Alumni Membership status.
\asubsection{Alumni Membership Privileges}
Alumni Members shall receive the right to:
\begin{itemize}
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
\end{itemize}
\asubsection{Alumni Membership Evaluations}
Alumni Members are not subject any evaluation.
\asubsection{Alumni Membership Resignations}
There are no resignations associated with Alumni Membership status.
\asubsection{Alumni Membership Term}
Alumni Membership shall last indefinitely or until the member chooses to pursue Active Membership.

@@

	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting. A quorum of fifty-percent of the Total Number of Possible Votes is required for the elections to be official. All winners are notified of their election, and they immediately assume the office for the term of the election. Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.

@@

\asection{Impeachment}
\begin{enumerate}
	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
	\item The impeachment petition is then presented at an Executive Board Meeting. The member(s) initiating the petition present their case to the Executive Board. The Executive Board then questions the accused member of the allegations.
	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment. If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed. This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office. Votes shall be collected and counted as described in \ref{Balloted Vote}.
	\item A quorum of two-thirds of the Total Number of Possible Votes is necessary for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office. If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position. A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
\end{enumerate}

@@

% ARTICLE V - VOTING
\article{Voting}
This section outlines the different types of votes and ballots used to make House decisions and defines relevant terminology.
\asection{Definitions}
\asubsection{Total Number of Possible Votes}
The sum of the number of Active members eligible to vote (i.e. not on co-op)
\asubsection{Total Number of Votes Cast}
The Total Number of Votes Cast is defined as the total number of votes received for every voting option minus the number of abstentions.
\asubsection{Quorum}
A Quorum is defined by the minimum number of votes cast required for a vote to be official. It is a fraction or a percentage of the total number of possible votes. Any member present for an Immediate Vote or given a ballot who does not explicitly cast their vote is counted as an Abstention. A Quorum is reached if the Total Number of Votes Cast plus the number of Abstentions is equal to or exceeding the minimum number of votes required.
\asubsection{Proxy Ballot}
A Proxy Vote is defined as any ballot that was cast by one member on behalf of another member. Any member may cast a Proxy Vote for another member who is unable to actually participate in the vote. A Proxy Vote must be explicitly written down and signed by the member not in attendance. The count of all Proxy Vote must be recorded and announced in all votes. Proxy Votes are only permissible where explicitly stated, at the discretion of the person chairing the vote.
\asubsection{Abstention}
An Abstention is defined as a vote indicating a neutral position in the vote. A means to abstain must always be provided in a vote. Abstentions are counted towards a Quorum, but not towards the Total Number of Votes Cast used to determine if a vote passes or not.
\asubsection{Vote Counters}
Vote Counters are the chairperson of the vote, and two randomly selected members.

### 2014-05-16 bylaws.tex
fixed references, added makefile
housing eval, alumni membership, quorum fix

On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}. A Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.

@@

The Housing Evaluation process occurs during the academic year. It is performed late Fall Semester after the Introductory Evaluation and is led by the Evaluations Director. The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).

@@

A quorum of two-thirds of all Active (excluding Introductory Process Participants) Members is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

@@

A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year. All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.These requirements are detailed in Article V under expectations for each category of membership. These requirements must be completed before the Membership Evaluation occurs. A secret Simple Majority vote with a quorum of two-thirds of all Active members is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.

>>>>

On a member by member basis, this evaluation process determines if each Introductory member has successfully completed the Introductory Process requirements \ref{Expectations of an Introductory Member}. A Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.

@@

The Housing Evaluation process occurs during the academic year. It is performed late Spring Semester before or concurrently with the Membership Evaluation and is chaired by the Evaluations Director. The Housing Evaluation is used to recognize an individual’s contributions to the House and distribute Housing Points (see \ref{Housing Priority System}).

@@

A quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither Absentee nor Proxy votes are allowed.

@@

A quorum of members, on a member by member basis, ensures that each Active member has met the minimum requirements in order to continue as an Active member in the following year. All Active Members will be held to the requirements and evaluated unless they received an exemption from the Executive Board prior to the event.These requirements are detailed in Article V under expectations for each category of membership. These requirements must be completed before the Membership Evaluation occurs. A secret Simple Majority vote with a quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid. Neither absentee nor proxy votes are allowed. House may choose any of the Outcomes for each member.
